DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-04 paper/evaluation.tex

we test its ability by  running synthetic benchmarks
concurrently with the model. In each experiment, we run a single model
on a  number of cores, and a synthetic benchmark on the remaining idle
cores. The effects of the benchmarks can seen in Figure 9 and Table
VI.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/BenchmarkChart}
  \caption{ Effect of benchmarks on inferencing time. }
\end{figure}

>>>>

In each experiment, we run a single DNN model one core, and
co-scheduled an increasing number of the memory intensive synthetic
benchmark on the remaining idle cores.
Figure~\ref{fig:}
The effects of the benchmarks can seen in Figure 9 and Table VI.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/BenchmarkChart}
  \caption{Effect of benchmarks on inferencing time.}
  \label{fig:}
\end{figure}
